---
title: "Supplementary Material"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Supplementary Material}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r message = FALSE}
library(ggplot2)
library(plotly)
library(dplyr)
library(colorspace)
library(dittoSeq)
library(tidyseurat)
library(tidygate)

seurat_obj <- tidyomicsWorkshop::seurat_obj
```


Instead of filtering using a specified threshold, the gamma delta T cells could be interactively selected from the plot using the tidygate package.

```{r eval = FALSE}
seurat_obj |>

  join_features(
    features = c("CD3D", "TRDC", "TRGC1", "TRGC2", "CD8A", "CD8B" ), shape = "wide"

  ) |>

  mutate(signature_score =
           scales::rescale(CD3D + TRDC + TRGC1+ TRGC2, to=c(0,1)) -
           scales::rescale(CD8A + CD8B, to=c(0,1))
  ) |>

  mutate(gate = gate(x= UMAP_1, y=UMAP_2, 
    size = 0.1, 
    colour = signature_score
  ))

```

After the selection we could reload from a file the gate that was drawn, for reproducibility.

```{r}
seurat_obj |>

  join_features(
    features = c("CD3D", "TRDC", "TRGC1", "TRGC2", "CD8A", "CD8B" ), shape = "wide"

  ) |>

  mutate(signature_score =
           scales::rescale(CD3D + TRDC + TRGC1+ TRGC2, to=c(0,1)) -
           scales::rescale(CD8A + CD8B, to=c(0,1))
  ) |>

  mutate(gate = gate(x= UMAP_1, y=UMAP_2, 
    size = 0.1, 
    colour = signature_score,
    programmatic_gates  = tidyomicsWorkshop::gate_seurat_obj
  ))

```

The dataset can be filtered for just these cells using tidyverse `filter`.

```{r}
seurat_obj_gamma_delta <-
    
  seurat_obj |>

  join_features(
    features = c("CD3D", "TRDC", "TRGC1", "TRGC2", "CD8A", "CD8B" ), shape = "wide"

  ) |>

  mutate(signature_score =
           scales::rescale(CD3D + TRDC + TRGC1+ TRGC2, to=c(0,1)) -
           scales::rescale(CD8A + CD8B, to=c(0,1))
  ) |>

  mutate(gate = gate(UMAP_1, UMAP_2, programmatic_gates = tidyomicsWorkshop::gate_seurat_obj)) |>

  filter(gate == 1)
```

## CuratedAtlasQuery

We will explore the tidy interface for the CELLxGENE harmonised data exploration and download. Please install `CuratedAtlasQuery`

```{r, eval=FALSE}
job::job({
  remotes::install_github("stemangiola/CuratedAtlasQueryR")
  })
```
